Oral anticoagulants

### 2020-12-11 r_notebooks/exploring_oral_anticoagulants.Rmd
minor changes

```{r}
system.time(oac_gp_fcsts <-
              oac_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% incomplete_gp) %>%
              regionalJointFcsts())
oac_gp_fcsts %>%
  write_rds("../data/oac_gp_fcsts.rds")

oac_gp_cluster_fcsts <- 
  read_rds("../data/oac_gp_fcsts.rds")
```

@@

best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_gp_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

>>>>

```{r}
system.time(oac_gp_fcsts <-
              oac_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% incomplete_gp) %>%
              regionalJointFcsts())
oac_gp_fcsts %>%
  write_rds("../data/oac_gp_fcsts_1.rds")

oac_gp_cluster_fcsts <- 
  read_rds("../data/oac_gp_fcsts_1.rds")
```

@@

best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```
